*Supplementary Material 1*

### 2022-06-20 ms/si.Rmd
Don't need to add Phlebosia in si.Rmd anymore

```{r genera-diff-make}
# FIXME: need to update ppgi csv file
# Add one missing nothogenus
ppgi_taxonomy_mod <-
  bind_rows(
    ppgi_taxonomy,
    tibble(
      genus = "Phlebosia",
      notes = "Nothogenus"
    )
  )

# Verify that all accepted genera are accounted for
accepted_species %>%
  count(genus, name = "n_species") %>%
  anti_join(select(ppgi_taxonomy_mod, genus, notes), by = "genus") %>%
  verify(nrow(.) == 0, success_fun = success_logical)

# Make table of pteridocat genera not in PPGI
pteridocat_not_in_ppgi <-
  accepted_species %>%
  count(genus, name = "n_species") %>%
  left_join(select(ppgi_taxonomy_mod, genus, notes), by = "genus") %>%
  assert(not_na, notes) %>%
  assert(is_uniq, genus) %>%
  filter(notes != "original PPGI 2016") %>%
  transmute(
    diff = "pteridocat not in PPGI",
    genus,
    n_species
  ) %>%
  # Add notes
  left_join(
    select(pteridocat_ppgi_diff_notes, -n_species),
    by = c("diff", "genus")
  ) %>%
  assert(not_na, note)

# Make table of PPGI genera not in pteridocat
ppgi_not_in_pteridocat <-
  ppgi_taxonomy_mod %>%
  filter(notes == "original PPGI 2016",
         class == "Polypodiopsida") %>%
  anti_join(accepted_species, by = "genus") %>%
  count(genus) %>%
  transmute(
    diff = "PPGI not in pteridocat",
    genus
  ) %>%
  # Add notes
  left_join(
    pteridocat_ppgi_diff_notes, by = c("diff", "genus")
  ) %>%
  assert(not_na, note)

>>>>

```{r genera-diff-make}
# Verify that all accepted genera are accounted for
accepted_species %>%
  count(genus, name = "n_species") %>%
  anti_join(select(ppgi_taxonomy, genus, notes), by = "genus") %>%
  verify(nrow(.) == 0, success_fun = success_logical)

# Make table of pteridocat genera not in PPGI
pteridocat_not_in_ppgi <-
  accepted_species %>%
  count(genus, name = "n_species") %>%
  left_join(select(ppgi_taxonomy, genus, notes), by = "genus") %>%
  assert(not_na, notes) %>%
  assert(is_uniq, genus) %>%
  filter(notes != "original PPGI 2016") %>%
  transmute(
    diff = "pteridocat not in PPGI",
    genus,
    n_species
  ) %>%
  # Add notes
  left_join(
    select(pteridocat_ppgi_diff_notes, -n_species),
    by = c("diff", "genus")
  ) %>%
  assert(not_na, note)

# Make table of PPGI genera not in pteridocat
ppgi_not_in_pteridocat <-
  ppgi_taxonomy %>%
  filter(notes == "original PPGI 2016",
         class == "Polypodiopsida") %>%
  anti_join(accepted_species, by = "genus") %>%
  count(genus) %>%
  transmute(
    diff = "PPGI not in pteridocat",
    genus
  ) %>%
  # Add notes
  left_join(
    pteridocat_ppgi_diff_notes, by = c("diff", "genus")
  ) %>%
  assert(not_na, note)
